analysis

### 2022-10-24 r-analysis/analysis.Rmd

```{r load data}
load("data-raw/data_wdi.RData")

@@

```{r overview statistics: emissions per capita 2020}
data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

@@

```{r overview statistics: emissions by sector development 1970:2020 }
data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

@@

```{r overview statistics: emissions changes }

>>>>

```{r load data}
load("data-transf/data_base.RData")

#load("data-raw/data_kaya.RData")

@@

```{r overview statistics: emissions per capita development 1970:2020}
data_countries <- data_ghg %>% 
  group_by(ISO,country,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

@@

```{r overview statistics: emissions by sector development 1970:2020 }
data_countries <- data_ghg %>% 
  group_by(ISO,country,year,sector) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

@@

```{r overview statistics: emissions changes }
data_change <- data_ghg %>% 
  group_by(ISO,country,region_ar6_6,year) %>% 
  summarise(GHG=sum(GHG,na.rm=TRUE))

## in this next chunk I calculate 3 different types of changes for the time period 2010-2019

data_change <- data_change %>% 
  filter(year %in% c(2010,2019)) %>% 
  group_by(ISO,country) %>% 
  mutate(change_abs = last(GHG)-first(GHG),               ## absolute change, or the difference in emissions between t2 and t1
         change_rel = change_abs/first(GHG),              ## relative change, or the ratio of absolute change to emissions in t1
         change_avg_annual = ((last(GHG)/first(GHG))^(1/(2019-2010))-1)) ## average annual change using the CGAR formula
